---
title: "`r params$docTitle`"
date: "`r format(Sys.Date())`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    fig_caption: false
params:
    docTitle: "BRICK Input Prices"
    file: "BRICK_input_price_report.csv"
    path: "C:/Users/ricardar/Documents/Results/BRICK/adaptCarrierPrices/calibration_2026-02-26_12.21.58/"
    scenNames: NULL
    name: ""
    region: ""
---

```{r setup, include=FALSE}
# nolint start: undesirable_function_linter.
library(dplyr, include.only = c("%>%", "across", "any_of", ".data", "filter", "mutate",
                                "select", "where"))
# nolint end

knitr::opts_chunk$set(
  echo = FALSE,
  error = TRUE,
  message = FALSE,
  warning = FALSE
)
```

```{r set variables, check existence of first file}
# Assemble all file paths
filePath <- file.path(params$path, params$file)

# Get country to EU9 regionmapping
regionmappingFull <- madrat::toolGetMapping("regionmappingEU27as9.csv", type = "regional", where = "mredgebuildings")
regionmapping <- regionmappingFull %>%
  select("CountryCode", "RegionCode") %>%
  filter(.data$RegionCode != "ROW")

# Check if at least one file in the given paths exists
if (!any(file.exists(filePath))) {
  message("No BRICK_input_price_report.csv file found.\n",
          "BRICK_input_price_report.csv can be produced by running 'reportPriceInput.R'.")
  knitr::knit_exit()
}
```

```{r function taken from mredgebuildings}

eur2usd <- function(x, year, iso3c) {
  year <- min(2023, year)
  tryCatch(
    GDPuc::convertSingle(x = x,
                         iso3c = iso3c,
                         year = year,
                         unit_in = paste("constant", year, "EUR"),
                         unit_out = "constant 2017 Int$PPP"),
    error = function(e) {
      if (grepl("No information in source .+ for countries in 'gdp'\\.",
                e$message)) {
        x
      } else {
        e
      }
    },
    warning = function(w) {
      if (grepl("NAs have been generated for countries lacking conversion factors",
                w$message)) {
        x
      } else {
        w
      }
    }
  )
}
```

```{r read in data}
data <- utils::read.csv(filePath)

singleCountries <- length(unique(data$region)) == length(unique(regionmapping$CountryCode))
```

# Carrier prices

```{r plot carrier prices}
showAnalysisPlot("line", data, "carrierPrice", "value",
                 color = "carrier", facets = NULL, rprt = "region", xname = "ttot",
                 ylabName = "Carrier price in [US$/kWh]", filterRows = NULL, include0onY = TRUE, linetype = "carrier")
```

# Price ratios

## With respect to gas only

```{r plot price ratios gas}
dataGasRatio <- data %>%
  filter(.data$carrier == "gases")

if (isTRUE(singleCountries)) {
  dataGasRatio <- left_join(dataGasRatio, regionmapping, by = c(region = "CountryCode"))
  rprtThis <- "RegionCode"
} else {
  dataGasRatio <- left_join(dataGasRatio, regionmapping, by = c(region = "RegionCode"))
  rprtThis <- NULL
}
  
showAnalysisPlot("line", dataGasRatio, "ratioElec", "value",
                 color = "region", facets = NULL, rprt = rprtThis, xname = "ttot",
                 ylabName = "Price ratio of electricity/gases", filterRows = NULL, include0onY = TRUE, linetype = "carrier")
```

## With respect to various carriers

```{r plot price ratios}
showAnalysisPlot("line", data, "ratioElec", "value",
                 color = "carrier", facets = NULL, rprt = "region", xname = "ttot",
                 ylabName = "Price ratio of electricity/given carrier",
                 filterRows = NULL, include0onY = TRUE, linetype = "carrier")
```

# Price ratio by heat pump sale shares

## All regions

```{r plot price ratio vs heat pump sale shares}

dataHpsales <- data %>%
  filter(.data$variable %in% c("ratioElec", "hpsalesShare"),
         .data$ttot %in% c(2000, 2005, 2010, 2015, 2020, 2022)) %>%
  group_by(across(-all_of("value"))) %>%
  summarise(value = mean(.data$value), .groups = "drop")

# carriers <- setdiff(unique(dataHpsales$carrier), NA)
carriers <- "gases"

allData <- list()

for (cr in carriers) {
  thisHpData <- dataHpsales %>%
    filter(.data$carrier == cr | is.na(.data$carrier)) %>%
    select(-"carrier") %>%
    pivot_wider(names_from = "variable") %>%
    filter(is.finite(.data$ratioElec), is.finite(.data$hpsalesShare)) %>%
    pivot_longer(cols = "ratioElec", names_to = "variable")
  allData[[cr]] <- thisHpData
  
  showAnalysisPlot("scatter", thisHpData, "ratioElec", "value",
                   xlabName = "Share of heat pumps in heating system sales",
                   ylabName = "Price ratio of electricity/given carrier",
                   color = "region", facets = NULL, rprt = "ttot", xname = "hpsalesShare",
                   filterRows = NULL, include0onY = TRUE, shape = "region")
  
}
```

## Selected regions

```{r plot price ratio vs hp sale shares, selected regions}

if (isTRUE(singleCountries)) {

  selectRegions <- c("FIN", "SWE", "DEU", "NLD", "EST", "POL", "ESP")
  
  dataHpsales <- data %>%
    filter(.data$variable %in% c("ratioElec", "hpsalesShare"),
           .data$ttot %in% c(2000, 2005, 2010, 2015, 2020, 2022),
           .data$region %in% selectRegions) %>%
    group_by(across(-all_of("value"))) %>%
    summarise(value = mean(.data$value), .groups = "drop")
  
  # carriers <- setdiff(unique(dataHpsales$carrier), NA)
  carriers <- "gases"
  
  allData <- list()
  
  for (cr in carriers) {
    thisHpData <- dataHpsales %>%
      filter(.data$carrier == cr | is.na(.data$carrier)) %>%
      select(-"carrier") %>%
      pivot_wider(names_from = "variable") %>%
      filter(is.finite(.data$ratioElec), is.finite(.data$hpsalesShare)) %>%
      pivot_longer(cols = "ratioElec", names_to = "variable")
    allData[[cr]] <- thisHpData
    
    showAnalysisPlot("scatter", thisHpData, "ratioElec", "value",
                     xlabName = "Share of heat pumps in heating system sales",
                     ylabName = "Price ratio of electricity/given carrier",
                     color = "region", facets = NULL, rprt = "ttot", xname = "hpsalesShare",
                     filterRows = NULL, include0onY = TRUE, shape = "region")
  }
    
}
```

```{r read in eurostat prices}
elecPrices <- readxl::read_xlsx("C:/Users/ricardar/Documents/Implementation Aids/BRICK/Data/nrg_pc_204__custom_19764442_spreadsheet.xlsx", sheet = "Sheet 7", skip = 11)[2:44, ] %>%
  select(-matches("\\.\\.\\.\\d{1,2}")) %>%
  rename(region = "TIME") %>%
  mutate(across(matches("\\d{4}-S\\d{1}"), ~ as.numeric(ifelse(.x == ":", NA, .x)))) %>%
  pivot_longer(matches("\\d{4}-S\\d{1}"), names_to = "time") %>%
  separate_wider_delim("time", "-", names = c("year", "semester")) %>%
  group_by(across(-all_of(c("semester", "value")))) %>%
  summarise(value = mean(.data$value, na.rm = TRUE), .groups = "drop") %>%
  mutate(carrier = "elec", year = as.numeric(.data$year))

gasPrices <- readxl::read_xlsx("C:/Users/ricardar/Documents/Implementation Aids/BRICK/Data/nrg_pc_202__custom_19764417_spreadsheet.xlsx", sheet = "Sheet 7", skip = 11)[2:37, ] %>%
  select(-matches("\\.\\.\\.\\d{1,2}")) %>%
  rename(region = "TIME") %>%
  mutate(across(matches("\\d{4}-S\\d{1}"), ~ as.numeric(ifelse(.x == ":", NA, .x)))) %>%
  pivot_longer(matches("\\d{4}-S\\d{1}"), names_to = "time") %>%
  separate_wider_delim("time", "-", names = c("year", "semester")) %>%
  group_by(across(-all_of(c("semester", "value")))) %>%
  summarise(value = mean(.data$value, na.rm = TRUE), .groups = "drop") %>%
  mutate(carrier = "gases", year = as.numeric(.data$year))

elecPricesNC <- readxl::read_xlsx("C:/Users/ricardar/Documents/Implementation Aids/BRICK/Data/nrg_pc_204__custom_19764442_spreadsheet.xlsx", sheet = "Sheet 9", skip = 11)[2:44, ] %>%
  select(-matches("\\.\\.\\.\\d{1,2}")) %>%
  rename(region = "TIME") %>%
  mutate(across(matches("\\d{4}-S\\d{1}"), ~ as.numeric(ifelse(.x == ":", NA, .x)))) %>%
  pivot_longer(matches("\\d{4}-S\\d{1}"), names_to = "time") %>%
  separate_wider_delim("time", "-", names = c("year", "semester")) %>%
  group_by(across(-all_of(c("semester", "value")))) %>%
  summarise(value = mean(.data$value, na.rm = TRUE), .groups = "drop") %>%
  mutate(carrier = "elec", year = as.numeric(.data$year))

gasPricesNC <- readxl::read_xlsx("C:/Users/ricardar/Documents/Implementation Aids/BRICK/Data/nrg_pc_202__custom_19764417_spreadsheet.xlsx", sheet = "Sheet 9", skip = 11)[2:37, ] %>%
  select(-matches("\\.\\.\\.\\d{1,2}")) %>%
  rename(region = "TIME") %>%
  mutate(across(matches("\\d{4}-S\\d{1}"), ~ as.numeric(ifelse(.x == ":", NA, .x)))) %>%
  pivot_longer(matches("\\d{4}-S\\d{1}"), names_to = "time") %>%
  separate_wider_delim("time", "-", names = c("year", "semester")) %>%
  group_by(across(-all_of(c("semester", "value")))) %>%
  summarise(value = mean(.data$value, na.rm = TRUE), .groups = "drop") %>%
  mutate(carrier = "gases", year = as.numeric(.data$year))
```

```{r combine eurostat prices}
eurostatPrices <- rbind(elecPrices, gasPrices) %>%
  left_join(regionmappingFull, by = c(region = "X")) %>%
  filter(.data$RegionCode != "ROW") %>%
  mutate(variable = "carrierPriceEuro")

eurostatRatio <- eurostatPrices %>%
  pivot_wider(names_from = carrier) %>%
  mutate(value = .data$elec / .data$gases,
         variable = "ratioElec", .keep = "unused")

eurostatPricesUSD <- eurostatPrices %>%
  mutate(year = as.character(.data$year)) %>%
  mutate(value = unlist(Map(eur2usd,
                            x = .data$value,
                            year = .data$year,
                            iso3c = .data$CountryCode)),
         variable = "carrierPrice")

eurostatRatioUSD <- eurostatPricesUSD %>%
  pivot_wider(names_from = carrier) %>%
  mutate(value = .data$elec / .data$gases, variable = "ratioElec", .keep = "unused")

eurostatPricesNC <- rbind(elecPricesNC, gasPricesNC) %>%
  left_join(regionmappingFull, by = c(region = "X")) %>%
  filter(.data$RegionCode != "ROW") %>%
  mutate(variable = "carrierPriceNC")

lcu2usd <- data.frame(region = unique(eurostatPricesNC$CountryCode)) %>%
    mutate(lcu2usd = GDPuc::toolConvertSingle(1, .data$region, 2015,
                                              unit_in = "current LCU",
                                              unit_out = "constant 2017 Int$PPP"))

vat <- 1.2

eurostatPricesUSDfromNC <- eurostatPricesNC %>%
  mutate(year = as.character(.data$year)) %>%
  left_join(lcu2usd, by = c(CountryCode = "region")) %>%
  mutate(value = .data$value / vat * .data$lcu2usd, # lcu/kWh to usd/kWh
         .keep = "unused",
         variable = "carrierPrice",
         year = as.numeric(.data$year))

eurostatRatioUSDfromNC <- eurostatPricesUSDfromNC %>%
  pivot_wider(names_from = carrier) %>%
  mutate(value = .data$elec / .data$gases,
         variable = "ratioElec",
         .keep = "unused")
```

# Price comparisons

## Comparison to Eurostat prices in Euro

### Eurostat prices

```{r plot Eurostat prices}
showAnalysisPlot("line", eurostatPrices, "carrierPriceEuro", "value",
                 color = "carrier", facets = NULL, rprt = "region", xname = "year",
                 ylabName = "Carrier price in [Euro/kWh]", filterRows = NULL, include0onY = TRUE, linetype = "carrier")
```

### Comparison carrier price

```{r plot carrier price comparison}
if (isTRUE(singleCountries)) {
  dataComp <- eurostatPricesUSD %>%
    select(-"region", -"RegionCode") %>%
    rename(region = "CountryCode", ttot = "year") %>%
    mutate(ttot = as.numeric(.data$ttot), source = "EUROSTAT") %>%
    rbind(data %>%
            mutate(source = "IEA"))
} else {
  dataComp <- eurostatPricesUSD %>%
    select(-"region") %>%
    group_by(across(-all_of(c("CountryCode", "value")))) %>%
    summarise(value = mean(.data$value), .groups = "drop") %>%
    rename(region = "RegionCode", ttot = "year") %>%
    mutate(ttot = as.numeric(.data$ttot), source = "EUROSTAT") %>%
    rbind(data %>%
            mutate(source = "IEA"))
}

showAnalysisPlot("line", dataComp, "carrierPrice", "value",
                 color = "carrier", facets = NULL, rprt = "region", xname = "ttot",
                 ylabName = "Carrier price in [US$/kWh]", filterRows = NULL, include0onY = TRUE, linetype = "source")
```

### Comparison price ratio w.r.t. gas

```{r plot price ratio comparison}
if (isTRUE(singleCountries)) {
  dataGasRatioComp <- eurostatRatio %>%
    select(-"region") %>%
    rename(ttot = "year", region = "CountryCode") %>%
    mutate(ttot = as.numeric(.data$ttot), carrier = "gases", source = "EUROSTAT") %>%
    rbind(dataGasRatio %>%
            mutate(source = "IEA"))
} else {
  dataGasRatioComp <- eurostatRatio %>%
    select(-"region") %>%
    rename(ttot = "year") %>%
    mutate(region = .data$CountryCode, ttot = as.numeric(.data$ttot), carrier = "gases", source = "EUROSTAT") %>%
    rbind(dataGasRatio %>%
            mutate(source = "IEA", RegionCode = .data$region))
}


showAnalysisPlot("line", dataGasRatioComp, "ratioElec", "value",
                 color = "region", facets = NULL, rprt = "RegionCode", xname = "ttot",
                 ylabName = "Price ratio of electricity/gases", filterRows = NULL, include0onY = TRUE, linetype = "source")
```

## Comparison to Eurostat prices in National Currency

### Eurostat prices

```{r plot Eurostat prices from NC}
showAnalysisPlot("line", eurostatPricesUSDfromNC, "carrierPrice", "value",
                 color = "carrier", facets = NULL, rprt = "region", xname = "year",
                 ylabName = "Carrier price in [USD/kWh]", filterRows = NULL, include0onY = TRUE, linetype = "carrier")
```

### Comparison carrier price

```{r plot carrier price comparison from NC}
if (isTRUE(singleCountries)) {
  dataComp <- eurostatPricesUSDfromNC %>%
    select(-"region", -"RegionCode") %>%
    rename(region = "CountryCode", ttot = "year") %>%
    mutate(ttot = as.numeric(.data$ttot), source = "EUROSTAT") %>%
    rbind(data %>%
            mutate(source = "IEA"))
} else {
  dataComp <- eurostatPricesUSDfromNC %>%
    select(-"region") %>%
    group_by(across(-all_of(c("CountryCode", "value")))) %>%
    summarise(value = mean(.data$value), .groups = "drop") %>%
    rename(region = "RegionCode", ttot = "year") %>%
    mutate(ttot = as.numeric(.data$ttot), source = "EUROSTAT") %>%
    rbind(data %>%
            mutate(source = "IEA"))
}

showAnalysisPlot("line", dataComp, "carrierPrice", "value",
                 color = "carrier", facets = NULL, rprt = "region", xname = "ttot",
                 ylabName = "Carrier price in [US$/kWh]", filterRows = NULL, include0onY = TRUE, linetype = "source")
```

### Comparison price ratio w.r.t. gas

```{r plot price ratio comparison from NC}
if (isTRUE(singleCountries)) {
  dataGasRatioComp <- eurostatRatioUSDfromNC %>%
    select(-"region") %>%
    rename(ttot = "year", region = "CountryCode") %>%
    mutate(ttot = as.numeric(.data$ttot), carrier = "gases", source = "EUROSTAT") %>%
    rbind(dataGasRatio %>%
            mutate(source = "IEA"))
} else {
  dataGasRatioComp <- eurostatRatioUSDfromNC %>%
    select(-"region") %>%
    rename(ttot = "year") %>%
    mutate(region = .data$CountryCode, ttot = as.numeric(.data$ttot), carrier = "gases", source = "EUROSTAT") %>%
    rbind(dataGasRatio %>%
            mutate(source = "IEA", RegionCode = .data$region))
}

showAnalysisPlot("line", dataGasRatioComp, "ratioElec", "value",
                 color = "region", facets = NULL, rprt = "RegionCode", xname = "ttot",
                 ylabName = "Price ratio of electricity/gases", filterRows = NULL, include0onY = TRUE, linetype = "source")
```
