# Stock and flows

## Building stock

```{r stock vars}
tot <- "Stock|Buildings"
subsec <- c("Stock|Residential",
            "Stock|Commercial")
```

```{r StockSubsector}
showAreaAndBarPlots(data, vars = subsec, tot = tot, orderVars = "user", scales = "fixed")
```

### All buildings

### Residential
```{r residential stock vars}
tot <- "Stock|Residential"
heatingRes <- paste(tot, heating, sep = "|")
vintageRes <- paste(tot, vintage, sep = "|")
typeRes <- paste(tot, type, sep = "|")
locationRes <- paste(tot, location, sep = "|")
```

#### by building type
```{r Stock-Residential-(type)}
showAreaAndBarPlots(data, vars = typeRes, tot = tot, orderVars = "user", scales = "fixed")
walk(typeRes, showLinePlots, data = data)
```

#### by location
```{r Stock-Residential-(location)}
showAreaAndBarPlots(data, vars = locationRes, tot = tot, orderVars = "user", scales = "fixed")
walk(locationRes, showLinePlots, data = data)
```

#### by Construction cohort
```{r Stock-Residential-(vintage)}
showAreaAndBarPlots(data, vars = rev(vintageRes), tot = tot, orderVars = "user", scales = "fixed")
```

#### by Space heating
```{r Stock-Residential-(heating)}
showAreaAndBarPlots(data, vars = heatingRes, tot = tot, orderVars = "user", scales = "fixed")
walk(heatingRes, showLinePlots, data = data)
```

### Commercial

## Construction flow

```{r stock vars}
tot <- "Construction|Buildings"
subsec <- c("Construction|Residential",
            "Construction|Commercial")
```

```{r ConstructionSubsector}
showAreaAndBarPlots(data, vars = subsec, tot = tot, orderVars = "user", scales = "fixed")
```

### All buildings

### Residential
```{r residential construction vars}
tot <- "Construction|Residential"
heatingRes <- paste(tot, heating, sep = "|")
typeRes <- paste(tot, type, sep = "|")
locationRes <- paste(tot, location, sep = "|")
```

#### by building type
```{r Construction-Residential-(type)}
showAreaAndBarPlots(data, vars = typeRes, tot = tot, orderVars = "user", scales = "fixed")
walk(typeRes, showLinePlots, data = data)
```

#### by location
```{r Construction-Residential-(location)}
showAreaAndBarPlots(data, vars = locationRes, tot = tot, orderVars = "user", scales = "fixed")
walk(locationRes, showLinePlots, data = data)
```

#### by Space heating
```{r Construction-Residential-(heating)}
showAreaAndBarPlots(data, vars = heatingRes, tot = tot, orderVars = "user", scales = "fixed")
walk(heatingRes, showLinePlots, data = data)
```

### Commercial

## Renovation flow

```{r stock vars}
tot <- "Renovation|Buildings"
subsec <- c("Renovation|Residential",
            "Renovation|Commercial")
```

```{r RenovationSubsector}
showAreaAndBarPlots(data, vars = subsec, tot = tot, orderVars = "user", scales = "fixed")
```

### All buildings

### Residential
```{r residential Renovation vars}
tot <- "Renovation|Residential"
totBefore <- paste(tot, "Initial", sep = "|")
totAfter <- paste(tot, "Final", sep = "|") # for proper plotting
shellResAfter <- paste(totAfter, shell, sep = "|")
heatingResBefore <- paste(totBefore, heating, sep = "|")
heatingResAfter <- paste(totAfter, heating, sep = "|")
heatingResAfterZero <- paste(totAfter, heating0, sep = "|")
typeRes <- paste(tot, type, sep = "|")
locationRes <- paste(tot, location, sep = "|")
identReplRes <- paste(tot, c("Heating|Identical replacement", "Change of heating system"), sep = "|")
identReplHsRes <- paste(tot, c("Identical replacement", "Change of heating system|Final"), sep = "|")
identReplHsRes <- lapply(heating, function(hsr) {
  paste(identReplHsRes, hsr, sep = "|")
})
```

#### by building type
```{r Renovation-Residential-(type)}
showAreaAndBarPlots(data, vars = typeRes, tot = tot, orderVars = "user", scales = "fixed")
walk(typeRes, showLinePlots, data = data)
```

#### by location
```{r Renovation-Residential-(location)}
showAreaAndBarPlots(data, vars = locationRes, tot = tot, orderVars = "user", scales = "fixed")
walk(locationRes, showLinePlots, data = data)
```

#### by building shell (final state)
```{r Renovation-Residential-(shell)}
showAreaAndBarPlots(data, vars = shellResAfter, orderVars = "user", scales = "fixed")
walk(shellResAfter, showLinePlots, data = data)
```

#### by Space heating (initial state)
```{r Renovation-Residential-(heatingBefore)}
showAreaAndBarPlots(data, vars = heatingResBefore, orderVars = "user", scales = "fixed")
walk(heatingResBefore, showLinePlots, data = data)
```

#### by Space heating (final state)
```{r Renovation-Residential-(heatingAfter)}
showAreaAndBarPlots(data, vars = heatingResAfter, orderVars = "user", scales = "fixed")
```

#### by Space heating (final state, with zero renovation)
```{r Renovation-Residential-(heatingAfter)}
showAreaAndBarPlots(data, vars = heatingResAfterZero, orderVars = "user", scales = "fixed")
walk(heatingResAfterZero, showLinePlots, data = data)
```

#### by identical replacement or not
```{r Renovation-Residential-(identicalReplacement)}
showAreaAndBarPlots(data, vars = identReplRes, orderVars = "user", scales = "fixed")
```

#### by identical replacement and by heating system
```{r Renovation-Residential-(heating-identicalReplacement)}
showAreaAndBarPlots(data, vars = unlist(identReplHsRes), orderVars = "user", scales = "fixed")
walk(identReplHsRes, showAreaAndBarPlots, data = data, orderVars = "user", scales = "fixed")
```

### Commercial
