# Extended Plots

```{r prepare load full data}
# Determine number of iterations (code duplicate from reportCalibration())
dirPath <- params$path
allFiles <- list.files(path = dirPath,
                         pattern = paste0("calibration", "_\\d{1,3}\\.gdx"))
allIter <- sort(as.numeric(sub(".*_(\\d{1,3})\\.gdx$", "\\1", allFiles)))
allFiles <- paste0("calibration_", allIter, ".gdx")

tCalib <- readGdxSymbol(file.path(dirPath, "input.gdx"), "tcalib", asMagpie = FALSE)[["uni"]] %>%
  as.character() %>%
  as.numeric()

```

## Stock and flow deviation

```{r load historic and model data for stocks, compute deviation}
#TODO: Need to flexibilise this depending on whether this is logit or optim calib
v_stockAll <- mip::getPlotData("v_stock", file.path(dirPath, allFiles)) %>%
  mutate(iteration = .data[["iteration"]] - 1)
p_stockCalibTarget <- mip::getPlotData("p_stockCalibTarget", file.path(dirPath, allFiles[1])) %>%
  mutate(iteration = NULL)

v_stockAll <- left_join(v_stockAll, p_stockCalibTarget,
                        by = setdiff(colnames(v_stockAll), c("iteration", "v_stock"))) %>%
  mutate(dev = .data[["v_stock"]] - .data[["p_stockCalibTarget"]])

stockDev <- v_stockAll %>%
  filter(.data$ttot %in% tCalib) %>%
  select(-"qty", -"bs", -"v_stock", -"p_stockCalibTarget") %>%
  rename(hsr = "hs", value = "dev") %>%
  mutate(variable = "stockDev") %>%
  tidyr::replace_na(replace = list(value = 0)) %>%
  dplyr::relocate("value", .after = last_col())
```


```{r load historic and model data for renovation, compute deviation}
#TODO: Need to flexibilise this depending on whether this is logit or optim calib
v_renovationAll <- mip::getPlotData("v_renovation", file.path(dirPath, allFiles)) %>%
  mutate(iteration = .data[["iteration"]] - 1)
p_renovationCalibTarget <- mip::getPlotData("p_renovationCalibTarget", file.path(dirPath, allFiles[1])) %>%
  mutate(iteration = NULL)

v_renovationAll <- dplyr::left_join(v_renovationAll, p_renovationCalibTarget,
                        by = setdiff(colnames(v_renovationAll), c("iteration", "v_renovation"))) %>%
  mutate(dev = .data[["v_renovation"]] - .data[["p_renovationCalibTarget"]])

renDevAll <- v_renovationAll %>%
  filter(.data$ttot %in% tCalib) %>%
  select(-"qty", -"bs", -"bsr", -"v_renovation", -"p_renovationCalibTarget")

renDev <- renDevAll %>%
  mutate(sgn = sign(.data[["dev"]])) %>%
  dplyr::group_by(across(any_of(c("iteration", "region", "loc", "typ", "inc", "hsr", "vin")))) %>%
  dplyr::summarise(value = sum(.data[["dev"]] ^ 2, na.rm = TRUE),
            valueSgn = sum(.data[["sgn"]] * .data[["dev"]] ^ 2, na.rm = TRUE),
            .groups = "drop") %>%
  mutate(sgn = sign(.data[["valueSgn"]]),
         value = .data[["sgn"]] * sqrt(abs(.data[["value"]]))) %>%
  select(-"sgn", -"valueSgn") %>%
  mutate(variable = "renDev") %>%
  tidyr::replace_na(replace = list(value = 0)) %>%
  dplyr::relocate("value", .after = last_col())

renDevAll <- renDevAll %>%
  dplyr::rename(value = "dev") %>%
  mutate(variable = "renDevAll") %>%
  tidyr::replace_na(replace = list(value = 0)) %>%
  dplyr::relocate("value", .after = last_col())

renTargetAll <- p_renovationCalibTarget %>%
  filter(.data[["ttot"]] %in% tCalib) %>%
  rename(target = "p_renovationCalibTarget") %>%
  group_by(across(all_of(c("region", "typ", "loc", "inc")))) %>%
  summarise(target = sqrt(sum(.data[["target"]] ^ 2, na.rm = TRUE)), .groups = "drop")

```

### Absolute stock deviation

```{r plot stock deviation}
.createCalibrationPlot(stockDev, "stockDev", outPath, outName = outName, color = "hsr",
                       facets = "vin")
```

### Absolute renovation deviation by final heating system

```{r plot renovation deviation}
.createCalibrationPlot(renDev, "renDev", outPath, outName = outName, color = "hsr",
                       facets = "vin")
```

### Absolute renovation deviation by initial heating system

```{r plot renovation deviation by initial hs}
for (hsr in extendedPlots[["filterHsr"]]) {
  renDevAllFilter <- renDevAll[renDevAll["hsr"] == hsr, ]
  .createCalibrationPlot(renDevAllFilter, "renDevAll", outPath, outName = outName, color = "hs",
                         facets = "vin")
}
```

### Absolute renovation deviation for each initial heating system

```{r plot renovation deviation for all initial hs}
.createCalibrationPlot(renDevAll, "renDevAll", outPath, outName = outName,
                       color = "hsr", facets = "vin")
```

### Comparison of identical replacement with zero flow

```{r compare deviation for identical replacement with zero}
allHs <- unique(renDevAll[["hs"]])
for (oneHs in allHs) {
  renDevAllHs <- renDevAll %>%
    filter(.data[["hs"]] == oneHs, .data[["hsr"]] %in% c("0", "ehp1", oneHs))
  .createCalibrationPlot(renDevAllHs, "renDevAll", outPath, outName = outName,
                         color = "hsr", facets = "vin", keepCol = "hs")
}
```

## Total stocks and flows

### Comparison of identical replacement with zero flow

```{r compare identical replacement with zero}
allHs <- unique(v_renovationAll[["hs"]])
for (oneHs in allHs) {
  renAllHs <- v_renovationAll %>%
    filter(.data$ttot %in% tCalib) %>%
    select(-"qty", -"bs", -"bsr", -"p_renovationCalibTarget", -"dev") %>%
    rename(value = "v_renovation") %>%
    mutate(variable = "renAllHs") %>%
    relocate("value", .after = last_col()) %>%
    filter(.data[["hs"]] == oneHs, .data[["hsr"]] %in% c("0", "ehp1", oneHs))
  .createCalibrationPlot(renAllHs, "renAllHs", outPath, outName = outName,
                         color = "hsr", facets = "vin", keepCol = "hs")
}
```
